Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-05 measurements.tex
Details about measurements setup

With the testbed and setups from the previous sections, we
proceed to obtain the measurements.

\subsection{Goodput}
Short intro

\subsubsection{Encoding}
%\includepdf[pages={31-32,38,40}]{images/raspberry.pdf}

% \begin{figure}[ht!]
% \centering
% \includegraphics[width=0.7\textwidth]{}
% \caption{Gooput measurements for the \ac{Raspi} 1. $q = 2$}
% \label{goodput_enc_rasp1}
% \end{figure}

\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.2\textwidth]{images/rasp1_good_vs_g_enc_gf2.pdf}
        \caption[]%
        {{\small $q = 2$}}    
        \label{fig:mean and std of net14}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}  
        \centering 
        \includegraphics[width=1.2\textwidth]{images/rasp1_good_vs_g_enc_gf256.pdf}
        \caption[]%
        {{\small $q = 2^8$}}    
        \label{fig:mean and std of net24}
    \end{subfigure}
    \vskip\baselineskip
    \begin{subfigure}[b]{0.475\textwidth}   
        \centering 
        \includegraphics[width=1.2\textwidth]{images/rasp1_good_vs_B_enc_gf2.pdf}
        \caption[]%
        {{\small $q = 2$}}    
        \label{fig:mean and std of net34}
    \end{subfigure}
    \quad
    \begin{subfigure}[b]{0.475\textwidth}   
        \centering 
        \includegraphics[width=1.2\textwidth]{images/rasp1_good_vs_B_enc_gf256.pdf}
        \caption[]%
        {{\small $q = 2^8$}}    
        \label{fig:mean and std of net44}
    \end{subfigure}
    \caption[ The average and standard deviation of critical parameters ]
    {\small Encoder goodput measurements for the \ac{Raspi} 1} 
    \label{fig:mean and std of nets}
\end{figure*}

\subsubsection{Decoding}
%\includepdf[pages={29-30,34,36}]{images/raspberry.pdf}

>>>>

With the testbed, methodology and setups from the previous sections, we
proceed to obtain the measurements for the \ac{Raspi} 1 and 2 platforms.
We consider the following set of parameters for our study:
For all the codes, we use $g = [16,\ 32,\ 64,\ 128,\ 256,\ 512]$
and $q = [2,\ 2^8]$. For the non-optimized multicore implementations
and cases when the generation size is varied $B = 1600\ bytes$.
We consider a setup where we only vary the packet size,
$B = [64,\ 128,\ 256,\ 512,\ 1024,\ 2048,\ 4096,\ 8192,\ 16384,\ 32768
,\ 65536,\ 131072]\ bytes$ with a generation size fixed on $g = [16,\ 128]$
to see computing load that the \ac{Raspi} present in the low and high
packet size regimes. We considered $B = 1536\ bytes$ for the optimized
multicore implementation. For \ac{SRLNC}, we considered
$d = [0.02,\ 0.1]$. For \ac{TSNC}, we considered excess packets,
$e = [8,\ 16]$, so that the budget is simply $b = g + e$. In all our
measurement reports, to simplify their review, we first presents the
results for the \ac{Raspi} 1 and later continue with the \ac{Raspi} 2.

\subsection{Goodput}
For the goodput, we separate the results according to their time benchmarks
as we did in Section \ref{sec:metrics} sicne their consider different
methodologies. We proceed first with the measurements related to the encoder
and later review the case of the decoder.

\subsubsection{Encoding}
Figs. \ref{fig:}

\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.2\textwidth]{images/rasp1_good_vs_g_enc_gf2.pdf}
        \caption[]%
        {{\small Goodput vs. Generation size for $GF(2)$}}    
        \label{fig:mean and std of net14}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}  
        \centering 
        \includegraphics[width=1.2\textwidth]{images/rasp1_good_vs_g_enc_gf256.pdf}
        \caption[]%
        {{\small Goodput vs. Generation size for $GF(2^8)$}}    
        \label{fig:mean and std of net24}
    \end{subfigure}
    \vskip\baselineskip
    \begin{subfigure}[b]{0.475\textwidth}   
        \centering 
        \includegraphics[width=1.2\textwidth]{images/rasp1_good_vs_B_enc_gf2.pdf}
        \caption[]%
        {{\small Goodput vs. Packet size for $GF(2)$}}    
        \label{fig:mean and std of net34}
    \end{subfigure}
    \quad
    \begin{subfigure}[b]{0.475\textwidth}   
        \centering 
        \includegraphics[width=1.2\textwidth]{images/rasp1_good_vs_B_enc_gf256.pdf}
        \caption[]%
        {{\small Goodput vs. Packet size for $GF(2^8)$}}    
        \label{fig:mean and std of net44}
    \end{subfigure}
    \caption[]
    {\small Encoder goodput measurements for the \ac{Raspi} 1} 
    \label{fig:enc_good_rasp1}
\end{figure*}

\subsubsection{Decoding}
